What We Eval in the Shadows

### 2021-04-05 paper/main.tex
Calls -> call sites

This section focuses on CRAN packages and reports statistics about the usage of
\eval. There are \PkgEvalCallSites calls to \eval in \PkgPackages packages.
These represent \PkgPackagesRatio of all packages or \PkgCodeRatio of the
entire code size of CRAN. Over half of the packages have less than 3 \eval
call sites and except \MaxEvalCallSitesPackage (\MaxEvalCallSitesCount \eval
calls), all packages contain less than \MaxEvalCallSitesRest \eval call sites
(\cf Fig~\ref{fig:pkgs-eval-callsites-hist}) These \eval calls appear in
\PkgFunsWithEval R functions (\CranFunsWithEvalRatio of all R functions in
CRAN).

>>>>

This section focuses on CRAN packages and reports statistics about the usage of
\eval. There are \PkgEvalCallSites call sites to \eval in \PkgPackages
packages.  These represent \PkgPackagesRatio of all packages or \PkgCodeRatio
of the entire code size of CRAN. Over half of the packages have less than 3
\eval call sites and except \MaxEvalCallSitesPackage (\MaxEvalCallSitesCount
\eval calls), all packages contain less than \MaxEvalCallSitesRest \eval call
sites (\cf Fig~\ref{fig:pkgs-eval-callsites-hist}) These \eval calls appear in
\PkgFunsWithEval R functions (\CranFunsWithEvalRatio of all R functions in
CRAN).
